2024 US Presidential Election Forecast Model

### 2024-11-04 paper/paper.qmd
Update by Doran
-Update paper.qmd, paper.pdf, and references.bib
-Update the new clean_data with no NA value

## Sample Data

@@

cleaned_data |>
  select(everything()) |>      # Select the first 3 columns
  head(5) |>
  kable(
    col.names = names(cleaned_data)[1:ncol(cleaned_data)],  # Automatically get the first 3 column names to match data
    booktabs = TRUE
  )
```

@@

## Population, Frame, and Sample

-Population:

-Frame:

-Sample:
a topline sample size of at least 100

## Sample Recruitment Method

@@

-Strengths:

-Weaknesses:

## How is non-response handled

@@

### Advantages

### Disadvantages

@@

Access the Survey Here: https://docs.google.com/forms/d/e/1FAIpQLSclP877Z1gT9nANFAUPrOz_K6IV6HOQXicb_cL0gwPRzhzpJw/viewform?usp=sf_link

@@

    Male

    Female

    Non-binary/Third gender

    Prefer not to say

@@

    Kamala Harris

    Donald Trump

    Other

    Undecided

@@

    Democrat

    Republican

    Independent

    Other

    Prefer not to say

@@

    Very confident

    Somewhat confident

    Not very confident

@@

    Healthcare

    Economy

    Immigration

    Climate Change

    Education

    National Security

    Social Justice

    Other (please specify)

@@

    Daily

    Weekly

    Occasionally

    Rarely

    Never

>>>>

## Sample Clean Data

@@

cleaned_data |>
  select(answer,pct,pollster,methodology,sample_size) |>      # Select the first 3 columns
  head(5) |>
  kable(
    col.names = c("Answer","Percentage","Pollster","Methodology","Sample Size"),  # Automatically get the first 3 column names to match data
    booktabs = TRUE
  )
```

The @tbl-cleaned_data shows the 5 of all colunms.

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-nyt_data
#| tbl-cap: "Sample Siena/NYT Data"
#| warning: false

nyt_data |>
  select(everything()) |>
  head(5) |>
  kable(
    col.names = c("Pollster","Methodology","Population","Sample Size","Grade Rating","Pollscore"),
    booktabs = TRUE
  )
```

## Background and Intro
The New York Times/Siena College Poll is a collaborative effort between The New York Times and the Siena College Research Institute, renowned for its methodological rigor and accuracy. The @tbl-nyt_data above shows sample data of Seina/NYT from clean data, which contains some useful information. According to FiveThirtyEight's pollster ratings, this partnership holds a 3.0-star rating as shown @tbl-nyt_data, indicating high reliability. Based on the section Methodological standards from FAQS of FiveThirtyEight[@fivethirtyeightFAQ], "Pollsters must also be able to answer basic questions about their methodology, including but not limited to the polling mode used (e.g., telephone calls, text messages, online panels), the source of their sample, their weighting criteria and the source of the poll's funding. In most cases, a detailed written methodology statement is sufficient to satisfy this criterion, but we may contact pollsters directly to clarify methodological details and follow up occasionally to ensure the pollster is still meeting our standards." Their data will ensure that pollsters maintain methodological standards. More specific details about NYT/SEINA's methodology are discussed below.

## Population, Frame, and Sample
 - Population:
The target population comprises likely voters in the United States, focusing on those eligible and expected to participate in the upcoming election.

 - Frame:
The sampling frame is constructed from voter registration lists, which are comprehensive databases of registered voters across various states.

 - Sample:
A stratified random sample is drawn from the voter registration lists, ensuring representation across key demographics such as age, gender, race, education, and geographic location.A topline sample size of at least 100 [@fivethirtyeightFAQ].

## Sample Recruitment Method
Participants are recruited through a combination of landline and mobile phone calls(like the Methodology in @tbl-nyt_data). This dual approach addresses the decline in landline usage and aims to reach a broader demographic spectrum. The use of voter registration lists enhances the likelihood of contacting registered voters, thereby improving the sample's representativeness.

@@

### Advantages
Enhances representativeness by ensuring all key subgroups are included.
Improves precision in estimates for specific subpopulations.

### Disadvantages
More complex and time-consuming compared to simple random sampling.
Requires accurate and up-to-date information on the stratification variables.
Handling Non-Response:

## How is non-response handled
Non-response is addressed through weighting adjustments. Post-stratification weights are applied to align the sample with known population parameters, such as age, gender, race, and education. This process mitigates biases arising from differential response rates among various demographic groups.

@@

### Advantages
 - Questions are crafted to be clear and unbiased, minimizing misinterpretation.
The questionnaire covers a broad range of topics, providing comprehensive insights into voter opinions.

### Disadvantages
 - The length of the questionnaire may lead to respondent fatigue, potentially affecting the quality of responses
 - The mode of administration (telephone interviews) might introduce social desirability bias, where respondents provide answers they perceive as socially acceptable rather than their true beliefs.

## Summary
Overall, the New York Times/Siena College Poll employs robust methodologies to ensure accurate and reliable insights into voter preferences and behaviors.

@@

Access the Survey Here: [US Presidential Election 2024: Voter Opinion and Key Issues Survey](https://docs.google.com/forms/d/e/1FAIpQLSclP877Z1gT9nANFAUPrOz_K6IV6HOQXicb_cL0gwPRzhzpJw/viewform?usp=sf_link)

@@

  \hspace{1cm}  Male

  \hspace{1cm}  Female

  \hspace{1cm}  Non-binary/Third gender

@@

  \hspace{1cm} Kamala Harris

  \hspace{1cm}  Donald Trump

  \hspace{1cm} Other

  \hspace{1cm}  Undecided

@@

  \hspace{1cm} Democrat

  \hspace{1cm} Republican

  \hspace{1cm}  Independent

  \hspace{1cm}  Other

@@

  \hspace{1cm}  Very confident

  \hspace{1cm}  Somewhat confident

  \hspace{1cm}  Not very confident

@@

  \hspace{1cm}  Healthcare

  \hspace{1cm}  Economy

  \hspace{1cm}    Immigration

  \hspace{1cm}  Climate Change

  \hspace{1cm}  Education

  \hspace{1cm}  National Security

  \hspace{1cm}  Social Justice

@@

  \hspace{1cm}  Daily

  \hspace{1cm}  Weekly

  \hspace{1cm}  Occasionally

  \hspace{1cm}  Rarely

  \hspace{1cm}  Never
